%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Nikhil Ranjan - 2014 Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Credits:
% https://news.ycombinator.com/item?id=3783538
% https://github.com/deedydas/Deedy-Resume
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{James}{O'Connor}{ \urlstyle{same}\url{http://jp-oconnor.com} \\
\href{mailto:k1454695@kingston.ac.uk}{james.oconnor@kingston.ac.uk} | Phone number masked}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}\label{sec:projects}

\subsection{Sentinel bot}\label{subsec:sentinel-bot}
\location{Twitter account which posts a Sentinel-2 satellite image every 30 minutes |} \href{http://twitter.com/sentinel\_bot}{http://twitter.com/sentinel\_bot}
\subsection{Personal blog}\label{subsec:personal-blog}
\location{Details aspects of my research, with explanations and tutorials |}\href{jamesoconnorkingston.wordpress.com}{jamesoconnorkingston.wordpress.com}
\subsection{Greyscaler}\label{subsec:greyscaler}
\location{Esoteric greyscaling algorithms via django web app |}\href{tinyurl.com/greyscaler}{tinyurl.com/greyscaler}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Expertise}\label{sec:expertise}
Python \\
Web Development (Django) \\
Predictive Modelling \\
Scikit-learn \\
Tensor Flow \\
OpenCV \\
Data Science \\
Databases \\
Image Processing \\
GIS/Mapping \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}\label{sec:links}
LinkedIn://  \href{https://www.linkedin.com/in/jamesoconnor12/}{\custombold{jamesoconnor12}} \\
Github:// \href{https://github.com/JamesOConnor}{\custombold{JamesOConnor}} \\
Twitter://  \href{https://twitter.com/James\_o\_connor1}{\custombold{\@James\_O\_Connor1}} \\
Wordpress://  \href{https://jamesoconnorkingston.wordpress.com}{\custombold{jamesoconnorkingston}} \\
Website://  \href{http://www.jp-oconnor.com}{\custombold{jp-oconnor.com}} \\
Kaggle://  \href{https://www.kaggle.com/james0c}{\custombold{james0c}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}\label{sec:skills}
\subsection{Computing}\label{subsec:computing}
\location{Languages}
Python \textbullet{} Linux \textbullet{} Django \textbullet{} Javascript \textbullet{} Imagemagick \textbullet{} MSSQL \textbullet{} Tensor Flow \textbullet{} git \linebreak
\location{Software packages}
Microsoft office \textbullet{} PyCharm IDE \textbullet{} ArcGIS/QGIS
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certification
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Languages}\label{sec:languages}
English (Native) \\
Spanish (Fluent) \\
French (Basic) \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}\label{sec:education}

\runsubsection{Kingston University London}
\descript{| PhD Candidate }
\location{September 2014 - Present | London, UK}
% Hacky fix for awkward extra vertical space
Thesis entitled 'Optimisation of aerial surveying from Unmanned Aerial Vehicles (UAVs)'.
Used custom image processing techniques developed using python OpenCV and photogrammetric packages for generation of detailed 3D data using Structure-from-Motion (SfM) photogrammetry.
Visualisation of large datasets using python's seaborn library.
\sectionsep

\runsubsection{University College London}
\descript{| Remote Sensing Masters | Distinction}
\location{September 2013 - September 2014 | London, UK}
Thesis investigated the accuracy of a radiative transfer model (Joint Research Council's two-stream inversion package).
Used large amounts of satellite data (MODIS) for comparison using custom python scripts.
\sectionsep

\runsubsection{Trinity College Dublin}
\descript{| Bachelor of Science | 2:1}
\location{September 2006 - September 2010 | Dublin, Ireland}
Thesis investigated biodiversity of urban pollinators in Dublin city centre and methods for promoting diversity.
Fieldwork skills in generating data for Environmental Impact Assessments.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}\label{sec:experience}

\runsubsection{Digital mapping assistant}
\location{ October 2014- present }
Provided technical support for classes of up to 70 undergraduates.
Engaged with students learning GIS and provided support
for a range of tasks assigned, from basic cartography in a GIS environment to web app development.
\sectionsep

\runsubsection{RSPSoc Student Representative \& SENSED Editor}
\linebreak
\location{June 2015 - present}
Have sat in council meetings and engaged in discussions on how to grow the society.
Organised and ran a 3 day conference at Kingston in March 2017 as part of my duties.
SENSED is a quarterly magazine produced by the society, of which I am an editor.
\sectionsep

\runsubsection{Developer - Quartz syndicate}
\linebreak
\location{November 2015 - present}
Used python scikit-learn toolbox to train models in prediction of outcomes of sporting events.
Specific tools include logistic regression, tree-based learners (LightGBM) and tensor-flow neural
networks to refine predictions.
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Papers}\label{sec:papers}

\begin{tabular}{rll}
2017	& Cameras and settings for aerial surveys in the geosciences: optimizing image data \\
&Progress in Physical Geography - \href{https://dx.doi.org/10.1177/0309133317703092}{DOI}
 \\
\end{tabular}
\sectionsep

\section{Selected Conference presentations}\label{sec:selected-conference-presentations}
\begin{tabular}{rll}
2017	     & European Geophysical Union AGM, Talk\\
&'Raw Image processing in structure-from-motion (SfM) surveying'\\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Societies}\label{sec:societies}

\begin{tabular}{rll}
2014 - Present	& Remote Sensing and Photogrammetry Society\\
\end{tabular}
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}